\thesistitle

### 2019-07-18 sections/background.tex
Better table stuff

\section{Clone Class}
As code clones are seen as one of the most harmful types of technical debt, they have been studied very extensively. A survey by Roy et al \cite{roy2007survey} states definitions for various important concepts in code clone research. In this survey, he mentions the concept ``clone pair'', which is \textit{a set of two code portions/fragments which are identical or similar to each other}. Furthermore, he defined ``clone class'' as \textit{the union of all clone pairs}. Apart from this, we use the definition ``clone instance'', which is a single code portion/fragment that is part of either a clone pair or clone class.

>>>>

\section{Defining clones}

\begin{table}[]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lllll@{}}
\toprule
\textbf{Symbol} & \textbf{Meaning} & \textbf{Description} & \textbf{Contents} & \textbf{Properties} \\ \midrule
\rowcolor[HTML]{EFEFEF}
S & Clone class collection & \begin{tabular}[c]{@{}l@{}}All clone classes that\\ have been found for a\\ certain software project.\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of clone\\ classes\end{tabular} & - \\
C & Clone class & \begin{tabular}[c]{@{}l@{}}A set of similar code fragments in\\ different locations.\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of clone\\ instances\end{tabular} & - \\
\rowcolor[HTML]{EFEFEF}
I & Clone instance & \begin{tabular}[c]{@{}l@{}}A code fragment that appears in\\ multiple locations.\end{tabular} & \begin{tabular}[c]{@{}l@{}}Set of cloned\\ nodes\end{tabular} & \begin{tabular}[c]{@{}l@{}}File (F): The file in which this\\ clone instance is found.\\ Range (R): The range this clone\\ instance spans.\end{tabular} \\
N & Node & \begin{tabular}[c]{@{}l@{}}A statement or declaration in a \\ codebase.\end{tabular} & Set of tokens & \begin{tabular}[c]{@{}l@{}}Range (R): The range this node\\ spans.\end{tabular} \\
R & Range & A part of a source code file. & Set of tokens & \begin{tabular}[c]{@{}l@{}}Begin line/column: The line and\\ column at which the range starts.\\ End line/column: The line and\\ column at which the range end.\end{tabular} \\
\rowcolor[HTML]{EFEFEF}
t & Token & \begin{tabular}[c]{@{}l@{}}Tokens are the basic lexical\\ building blocks of source code. \\ For this study, this is the smallest\\ relevant entity of a program.\end{tabular} & - & \begin{tabular}[c]{@{}l@{}}Range (R): The range this token\\ spans.\\ Category: Identifier, Keyword,\\ Literal, Separator, Operator,\\ Comment or Whitespace\end{tabular} \\ \bottomrule
\end{tabular}%
}
\caption{Clone related terminology and how it maps to the source code.}
\label{tab:clone-terminology}
\end{table}

\subsection{Clone Class}
As code clones are seen as one of the most harmful types of technical debt, they have been studied very extensively. A survey by Roy et al \cite{roy2007survey} states definitions for various important concepts in code clone research. In this survey, he mentions the concept ``clone pair'', which is \textit{a set of two code portions/fragments which are identical or similar to each other}. Furthermore, he defined ``clone class'' as \textit{the union of all clone pairs}. Apart from this, we use the definition ``clone instance'', which is a single code portion/fragment that is part of either a clone pair or clone class.
